---
title: "Kelp_condition_nuts"
author: "Wendel Raymond"
date: "April 12, 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Isotopes, nutrients, and summary data
This scripts will summarize isotope, nutrient and other non-spectral data from kelp tissues on POW.

```{r libraries}
library(ggplot2)
library(ggrepel)
library(dplyr)
library(LaCroixColoR)
theme_set(theme_classic())
```


## Data
```{r data}
iso <- read.csv("../Other Data/Kelp_CN_data.csv", header = TRUE, stringsAsFactors = FALSE)

nut <- read.csv("../Other Data/Water_nutrients_2018_All.csv", header = TRUE, stringsAsFactors = FALSE)

chl <- read.csv("../Other Data/Kelp_ChlC.csv", header = TRUE, stringsAsFactors = FALSE)

spec <- read.csv("../Other Data/kelp_spectra.csv", header = TRUE, stringsAsFactors = FALSE)

oce <- read.csv("../Other Data/Site_oceanography_2018_RAW.csv", header = TRUE, stringsAsFactors = FALSE)
```

color pallette
```{r}
pal <- lacroix_palette("PeachPear")
```

## Spectral data
Plot of representative N content blades reflectance
```{r spec plot}
ggplot(spec) +
  geom_line(aes(x = wv, y = low), lwd = 2, col = pal[1]) +
  geom_line(aes(x = wv, y = mid), lwd = 2, col = pal[4]) +
  geom_line(aes(x = wv, y = high), lwd = 2, col = pal[6]) +
  geom_vline(xintercept = 655, lty = "dashed") +
  geom_vline(xintercept = 670, lty = "dashed") +
  scale_x_continuous(limits = c(450, 750), breaks = seq(450, 750, 50)) +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 10)) +
  labs(x = "Wavelength (nm)", y = "% Reflectance") +
  theme(text = element_text(size = 32))
```

Plot of spec N and lab N
```{r obs v lab}
ggplot(chl) +
  geom_point(aes(x = Lab_N, y = Blade_N), size = 3, pch = 1) +
  geom_text_repel(aes(x = Lab_N, y = Blade_N, label = Site_code), nudge_x = 0.1, size = 8) +
  geom_abline(intercept = 0, slope = 1, lty = "dashed", lwd = 1.5) +
  scale_x_continuous(limits = c(0, 3.5), breaks = seq(0, 3.5, 0.5)) +
  scale_y_continuous(limits = c(0, 3.5), breaks = seq(0, 3.5, 0.5)) +
  labs(x = "% N Laboratory", y = "% N Spectral") +
  theme(text = element_text(size = 32))

summary(lm(chl$Blade_N ~ chl$Lab_N))
```

Plot spec N and water N
```{r obs v seawater}
ggplot(chl) +
  geom_point(aes(x = SeaW.N, y = Mean_N), size = 3, pch = 1) +
  geom_text_repel(aes(x = SeaW.N, y = Mean_N, label = Site_code), nudge_x = 0.01, size = 8) +
  geom_abline(intercept = 0.08101, slope = 3.39495, lwd = 1.5, lty = "dashed") +
  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  scale_y_continuous(limits = c(0, 3.5), breaks = seq(0, 3.5, 0.5)) +
  labs(x = "Seawater Nitrite + Nitrate (umol/L)", y = "% N Spectral") +
  theme(text = element_text(size = 32))

summary(lm(chl$Mean_N ~ chl$SeaW.N))
```


## Isotope data
```{r iso}
ggplot(iso) +
  geom_point(aes(x = del_C, y = del_N, color = percent_N), size = 4) +
  scale_color_gradientn(colours = rainbow(5)) +
  geom_text(aes(x = del_C, y = del_N, label = row.names(iso)), hjust = 0, nudge_x = 0.15) +
  scale_x_continuous(limits = c(-20.0, -10), breaks = c(-20, -18, -16, -14, -12, -10)) +
  scale_y_continuous(limits = c(4, 10), breaks = c(4, 5, 6, 7, 8 ,9, 10)) +
  labs(x = expression(delta~"C"), y = expression(delta~"N")) +
  
  theme(text = element_text(size= 32))
```

## Nutrient data
First need to filter data to what makes sense for this project.
1) All WR 2018_H/L sites

```{r nuts sum}
## reduce ##
nut.redu <- nut[c(1:29, 59:74, 88:95), ]
  
## Summarize ##
nut.sum <- nut.redu %>% 
  group_by(Site, Depth_m) %>% 
  summarise(Nitrate = mean(Nitrate_um.L),
            NitraNitri = mean(NitrateNitrite_um.L),
            Phosph = mean(Phos_um.L),
            Nitrate_sd = sd(Nitrate_um.L),
            NitraNitri_sd = sd(NitrateNitrite_um.L),
            Phosph_sd = sd(Phos_um.L))
```

## Other oceanography
```{r}

```


plots
```{r nut plots}
ggplot(nut.sum) +
  geom_col(aes(x = Site, y = Nitrate, fill = Depth_m), position = "dodge")
```

